%!TEX root = report.tex

\section{Group Report}

The project was a failure. The plan was to start the first sprint
in the first week of March and work our way through in 2 week sprints 
in order to finish as much of the project by the end of April as possible. 
In time for the original due date.

During February we meet twice in order to decide and agree on the
tools we were going to use, and to split up responsibilities. All
though all of us were present and got things like the GitHub
repository setup, we were already facing issues with members 
communication well bar none. The plan for the first sprint took far 
too long to make, and
was never completed.

In March although we started programming, we found it very difficult
to balance time between this project and all other assignments. Thus
resulting in some slacking and and falling behind schedule. During 
this time the Coronavirus situation was also getting serious and all
of us being international students were concerned about what it was 
going to be like for us. The added stress of deciding whether to go 
home or to stay compounded by what our families were saying and with
countries starting to close their borders, some even for 
repatriating citizens.

As all of us started to self quarantine in preparation to return to
our respective countries, Communication between group members became
more strained. This resulted in members working on different parts 
of the project without planning compatibility between each other.

In April when we got settled in back home and we continued working 
on the project, we realised not all of us knew how to use git very
well and faced issues with branching and even uploading to 
GitHub. Although we did get the GitHub issue mostly sorted out in 
May. Yet with the lack of communication we were not sure who had 
done what and how much or even how so we ended up with 2 separate 
builds of the program. One had better game logic and 
visible graphics
and the other with better graphic but no game logic

In May when we were finally Communicating better and got the GitHub 
issue sorted out, we noticed the 2 very different builds and by this
time there was not enough time to combine the best parts of the
two as that required significant amount of work.

In the end there are 2 somewhat working source files that are not
documented well. Neither of which meet even the requirements set 
forth for the 1st sprint. And all other deliverables are also lacking. In doing all of this the Agile Sprint development cycle 
also got thrown out of the window. Thus the project was a failure.